% Ocean Engineering (Elsevier) submission skeleton based on the official
% elsarticle templates placed under `paper/elsarticle/`.
%
% Source of truth: edit `paper/sections/*.md`, then propagate changes here.
%
% Note: this project intentionally keeps the LaTeX tree buildable from the repo root.
\documentclass[authoryear,preprint,12pt]{elsarticle}

%% Submission baseline for OE in this repo: single-column preprint.
%% Optional review spacing can be enabled if needed:
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% LaTeX double-column formatting is permitted by OE guide when needed, e.g.:
%% \documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,5p,times,authoryear]{elsarticle}

%% The amssymb package provides various useful mathematical symbols.
\usepackage{amssymb}
%% The amsmath package provides various useful equation environments.
\usepackage{amsmath}

%% Line numbers (recommended for review).
\usepackage{lineno}

%% For figures, graphicx is loaded by elsarticle.cls; keep it explicit for clarity.
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage{url}

\makeatletter
% Allow building both from repo root and from within `paper/latex/`.
\def\input@path{{paper/latex/}{paper/latex/sections/}}
\makeatother

\modulolinenumbers[5]
\journal{Ocean Engineering}

\begin{document}
\begin{frontmatter}

\title{Design and Characterization of a Mission-Oriented Self-Suspending Underwater Platform with Anisotropic Permeability-Corrected Dynamics and Experimental Identification}

% TODO: Replace with real author list and affiliations (official elsarticle style).
\author[inst1]{First Author\corref{cor1}}
\author[inst1]{Second Author}
\cortext[cor1]{Corresponding author.}
\ead{corresponding.author@example.com}
\affiliation[inst1]{organization={Affiliation},
            addressline={},
            city={},
            postcode={},
            state={},
            country={}}

\begin{abstract}
Underwater corner reflectors are used as passive high-contrast markers for marine detection and localization tasks, and their deployment reliability depends on the carrier platform. This paper presents the design and characterization of a mission-oriented self-suspending underwater platform developed for corner-reflector deployment. The platform is required to pass through a horizontal-launch to vertical-stabilization transition before reaching its working posture; therefore, platform architecture, mass-buoyancy arrangement, and deployment workflow are treated as primary engineering contributions.

For this transition phase, an anisotropic permeability-corrected 3-DOF dynamic model is developed with three physically interpretable coupling parameters, \texttt{mu\_x}, \texttt{mu\_z}, and \texttt{mu\_theta}, to represent directional internal-water coupling effects. CFD-derived static hydrodynamic mappings are used as model evidence for force and moment replacement logic, while rotational damping is retained as an identification-oriented term. A closed validation chain is established through free-decay identification, out-of-sample simulation-to-experiment evaluation, and sensitivity-based envelope analysis. The identification and evaluation stages use consistent initialization and condition-level split rules to reduce leakage risk and support fair sim-real comparison.

The resulting platform-model framework provides consistent reconstruction of transition behavior and practical guidance for deployment-oriented design and parameter selection. Conclusions are explicitly limited to the current geometry, mass distribution, and actuation strategy, and the workflow is organized for reproducibility through protocolized preprocessing and condition-level split control.
\end{abstract}

%% Graphical abstract is optional for this journal and should be submitted
%% only when available as a separate asset.

%%Research highlights (also often uploaded as a separate file during submission).
\begin{highlights}
\input{highlights_items}
\end{highlights}

\begin{keyword}
Underwater platform \sep Mission-oriented deployment \sep Free-decay identification \sep CFD evidence \sep Added mass \sep Permeability correction
\end{keyword}

\end{frontmatter}

\linenumbers

\input{sections/01_introduction}
\input{sections/02_system_and_mission_scenario}
\input{sections/03_anisotropic_permeability_corrected_dynamics}

% TODO: Convert the remaining section drafts when ready.
\input{sections/04_cfd_to_model_mapping_and_validation}
\input{sections/05_parameter_identification_free_decay}
\input{sections/06_sim_real_validation}
\input{sections/07_sensitivity_and_design_implications}
\input{sections/08_conclusion_and_outlook}

\section*{Data availability}
The data that support the findings of this study are available in a public
repository [DOI/URL to be inserted before submission]. If specific subsets
cannot be openly shared, the corresponding restriction reason will be stated
explicitly in this section.

\section*{CRediT authorship contribution statement}
% TODO: Fill per Ocean Engineering Guide for Authors (CRediT roles).

\section*{Funding}
This research did not receive any specific grant from funding agencies in the
public, commercial, or not-for-profit sectors.

\section*{Declaration of generative AI and AI-assisted technologies in the manuscript preparation process}
% Include this section only if generative AI tools were used during manuscript
% preparation. If no generative AI tools were used, remove this section.
% Example (when applicable): During the preparation of this work, the authors
% used [NAME OF TOOL / SERVICE] in order to [REASON]. After using this
% tool/service, the authors reviewed and edited the content as needed and take
% full responsibility for the content of the publication.

\section*{Declaration of competing interest}
The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

\section*{Acknowledgements}
% TODO: Place acknowledgements in this section, directly before the reference list.

% NOTE: Use the journal's author-year reference style.
% Enforce using the local official BST file under `paper/elsarticle/`.
% NOTE: Use workspace-relative paths so latexmk can pre-check file existence.
\bibliographystyle{paper/elsarticle/elsarticle-harv}
\bibliography{paper/latex/references}

\end{document}
