% Synced from: paper/sections/01_introduction.md
\section{Introduction}

Underwater corner reflectors are widely utilized as passive, high-contrast markers for marine detection and localization tasks. In practical deployment operations, system reliability depends not only on the packaging of the reflector itself but also on the post-release behavior of its carrier platform. In the scenario considered in this study, a custom miniature platform is released in a compact, near-horizontal configuration with a nonzero initial velocity and must autonomously settle into a stable, near-vertical working posture. This horizontal-release to vertical-stabilization transition is mission-defining: the payload becomes operational only after the platform reaches the working posture with bounded overshoot and a bounded terminal pitch rate, under strict constraints imposed by packaging, buoyancy layout, and the deployment procedure.

Recent studies on underwater corner reflectors have predominantly addressed acoustic scattering characteristics and structural design choices to enhance detectability and target strength. For example, \citet{Luo2020AirCavityCornerReflector} proposed an air-cavity method to increase target strength, and \citet{Chu2022EightGridAirCavityCornerReflector} examined scattering characteristics of an eight-grid air-filled cavity corner reflector. \citet{Xiao2025CornerReflectorLinearArrays} investigated the scattering behavior of corner-reflector linear arrays, while \citet{Luo2025ElasticLossCornerReflector} analyzed elastic-loss effects in acoustic echoes from corner reflectors. \citet{Du2023MetasurfaceCornerReflector} studied metasurface-assisted mechanisms for scattering modulation. These works largely treat the reflector as the primary design object and typically do not address the post-release dynamics of the carrier platform.

Regarding release and separation dynamics, \citet{Wang2024AUVInitialSeparation} numerically analyzed separation motion and hydrodynamic influencing parameters in an initial separation phase, and \citet{Deng2024PayloadReleaseAttitudeStabilization} investigated attitude stabilization of an unmanned underwater vehicle during payload release. \citet{Zhang2025RetrievalCaptureMechanism} reported the design and analysis of an underwater retrieval and capture mechanism. However, to our knowledge, for underwater corner-reflector deployment, dedicated reports that jointly (i) realize a miniature carrier platform and (ii) couple the horizontal-release to vertical-stabilization transition with rigorous experimental validation under mission-constrained release conditions remain limited.

Existing approaches for underwater vehicle motion modeling can be broadly categorized into high-fidelity computational fluid dynamics (CFD) simulations and reduced-order rigid-body dynamic models. \citet{Fossen2011HandbookMarineCraft} provided a comprehensive formulation of marine craft hydrodynamics and motion control, which underpins many reduced-order models used for time-domain prediction. \citet{AminiForoushani2021HydrodynamicDerivativesCFD} used CFD analyses of synthetic standard dynamic tests to determine hydrodynamic derivatives of an ocean vehicle, and \citet{Chin2018OpenFrameROVVirtualReality} developed and experimentally validated an open-frame remotely operated vehicle (ROV) model for simulation and control. \citet{Xu2017InertialHydrodynamicROV} experimentally studied inertial hydrodynamic behaviors of a complex ROV. For permeable structures, \citet{Molin2011HydrodynamicModelingPerforated} reported hydrodynamic modeling considerations for perforated structures, and \citet{Mentzoni2019NumericalModelingPerforatedPlates} presented numerical modeling of perforated plates in oscillating flow. For parameter determination, \citet{Ross2004IdentificationUUVHydrodynamicCoefficients} identified underwater vehicle hydrodynamic coefficients using free-decay tests, and \citet{Sun2021NonlinearRollDampingFreeDecay} performed parameter identification using free-decay data for nonlinear roll damping.

Two key insights emerge from the above literature. First, a reduced-order model supported by CFD and standardized experiments provides a practical basis for repeated transition-phase evaluations, provided that its hydrodynamic closure is formulated consistently \citep{Fossen2011HandbookMarineCraft,AminiForoushani2021HydrodynamicDerivativesCFD,Ross2004IdentificationUUVHydrodynamicCoefficients}. Second, open-frame, perforated, or otherwise permeable structures can exhibit additional inertia-related mechanisms through internal flow and momentum exchange, and these mechanisms may depend strongly on permeability and geometry \citep{Molin2011HydrodynamicModelingPerforated,Mentzoni2019NumericalModelingPerforatedPlates,Xu2017InertialHydrodynamicROV}. However, a mission-oriented miniature deployment platform introduces a coupled challenge: the open structure required by packaging and release constraints can entrain internal water and yield direction-dependent inertia coupling during large-attitude transitions, while CFD-based static closure and experimentally identified damping must be combined without term double counting. These considerations motivate a compact transition-phase model with bounded, interpretable coupling parameters and a closed evidence chain from standardized free-decay identification to independent-condition validation and operating guidance.

To address these considerations, this study designs and fabricates a self-suspending miniature underwater platform tailored for underwater corner-reflector deployment and investigates its horizontal-release to vertical-stabilization transition. We develop an interpretable, planar three-degree-of-freedom (3-DOF) transition-phase model encompassing surge, heave, and pitch, in which directional internal-water inertia coupling is captured by three bounded, anisotropic permeability-corrected parameters ($\mu_x$, $\mu_z$, $\mu_\theta$). Static hydrodynamic forces and moments are closed using CFD-derived coefficient mappings, while rotational damping and the remaining dynamic parameters are identified from standardized free-decay experiments. With parameters held fixed, the resulting closed model is validated against independent conditions and is then used to delineate feasible initial-condition envelopes and provide practical operating guidance for the transition of the designed platform.

The main contributions and novel aspects of this work are summarized as follows.
{\renewcommand{\labelenumi}{(\roman{enumi})}
\begin{enumerate}
\item The design and physical realization of a mission-oriented, self-suspending miniature underwater platform and its tailored deployment procedure, providing a dedicated hardware solution for underwater corner-reflector placement.
\item An interpretable Fossen-style 3-DOF (surge--heave--pitch) transition-phase model that incorporates anisotropic permeability-corrected inertia coupling through bounded parameters ($\mu_x$, $\mu_z$, $\mu_\theta$), and a static hydrodynamic closure utilizing CFD-derived coefficient mappings.
\item Parameter identification including standardized free-decay experiments and out-of-sample validation of the closed model developed in (ii), followed by sensitivity analyses that delineate an initial-condition feasibility envelope and provide practical operating guidance for the horizontal-to-vertical transition phase of the platform designed in this study.
\end{enumerate}}

It should be noted that the scope of this study focuses specifically on the transitional phase from horizontal release to vertical stabilization. Aspects such as closed-loop depth control, long-term operational behavior, and broader mission logistics fall outside the current scope and are deferred to future work. Furthermore, the quantitative conclusions and operational envelopes derived herein are specific to the investigated platform configuration, including its geometry, mass-buoyancy distribution, and actuation strategy.

The remainder of this paper is organized as follows. Section 2 details the platform architecture and deployment scenario. Section 3 describes the experimental setup and data processing strategies for free-decay tests. Section 4 elaborates on the reduced-order dynamic model and the CFD-based hydrodynamic closure. Section 5 presents the parameter identification methodology and uncertainty diagnostics. Section 6 validates the integrated model against independent experimental data and analyzes discrepancy modes. Section 7 conducts a parametric analysis to provide operational guidelines for the current configuration. Finally, Section 8 summarizes the main conclusions and outlines future research directions.
